---
title: "Proj_NHANES"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## NHANES Project

```{r}
devtools::install_github("andrew-leroux/rnhanesdata", build = TRUE, 
                         build_opts = c("--no-resave-data", "--no-manual"), force = TRUE)

library(rnhanesdata)
```


```{r, process_accel_flags, eval=FALSE}
load("C:/Users/Zebin Wang/Desktop/HW1/Ciprian-Project/Covariate_C.rda")
load("C:/Users/Zebin Wang/Desktop/HW1/Ciprian-Project/Covariate_D.rda")
load("C:/Users/Zebin Wang/Desktop/HW1/Ciprian-Project/Flags_C.rda")
load("C:/Users/Zebin Wang/Desktop/HW1/Ciprian-Project/Flags_D.rda")
load("C:/Users/Zebin Wang/Desktop/HW1/Ciprian-Project/Mortality_2011_C.rda")
load("C:/Users/Zebin Wang/Desktop/HW1/Ciprian-Project/Mortality_2011_D.rda")
load("C:/Users/Zebin Wang/Desktop/HW1/Ciprian-Project/Mortality_2015_C.rda")
load("C:/Users/Zebin Wang/Desktop/HW1/Ciprian-Project/Mortality_2015_D.rda")
load("C:/Users/Zebin Wang/Desktop/HW1/Ciprian-Project/PAXINTEN_C.rda")
load("C:/Users/Zebin Wang/Desktop/HW1/Ciprian-Project/PAXINTEN_D.rda")
```
Mainly look at them:

```{r}
head(PAXINTEN_C)
head(Flags_C)
```

C,D: Basically different research projects (Different group of people)

Flags: Whether the band is used (data collected at the time)

Covariate: BMI, Race, Gender, Diabetes, etc. (We need to match on these parameters)

Mortality: Mortality is collected in two times: The research is done 2003-2004 (C) and 2005-2006 (D).

```{r}
head(Mortality_2011_C)
```

`Mortstat` is the "whether dead or not" judgment.

```{r}
head(Covariate_C)
```

Basically the model can be a glm Binomial model; I wonder if it is necessary to work on machine learning.

Can we smooth on (Flag * movement), and fit a glm binomial with that smooth function, then put other possible confounders in the structure?

I believe it is doable and I would suggest using a binomial regession (easier to interpret).
